\section{Processor Equivalence}
In this section, we will discuss the power equivalence problem.
\\
I will present the closed-form equal formula about the load from three different kind of injection position,load from corner,boundary and inner grid position in regular mesh.
\\
In addition, considering the unit core with or without the front-end processor,the data transportation schema can be considered as two situation with front-end  and without front-end transportation.

\vspace*{5pt}

For a homogeneous regular mesh, which can be collapsed into an equivalent node, the notation is presented as follows.\\

\begin{itemize}

\item $\alpha_{0}$: The load fraction assigned to the root processor.
\item $\alpha_{i}$: The load fraction assigned to the $i$th processor.
\item $\omega_{i}$: The inverse computing speed on the $i$th processor.
\item $\omega_{eq}$: The inverse computing speed on an equivalent node collapsed from a regular mesh.
\item $z_{i}$: The inverse link speed on the $i$th link.
\item $T_{cp}$: Computing intensity constant.The entire load can be transmitted in $z_{i}T_{cp}$ on the $i$th processor.
\item $T_{cm}$: Communication intensity constant.The entire load can be transmitted in $z_{i}T_{cm}$ seconds over the $i$th link.
\item $T_{f,m}$: The finish time of the whole regular network.Here $T_{f,m}$ is equal to $\omega_{eq}T_{cp}$.
\item $T_{f,0}$: The finish time for the entire divisible load solved on the root processor.Here $T_{f,0}$ is equal to $1 \times \omega_{0}T_{cp}$, that is $\omega_{0}T_{cp}$.

\end{itemize}
\vspace*{5pt}
\input{equalfrontend.tex}
\vspace*{5pt}
\input{equalnofrontend.tex}
\vspace*{5pt}
\input{equalcompare.tex}

